---
title: "module-B"
author: "dkillian"
date: "2020-12-08"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction

```{r}
library(ggplot2)

a <- data.frame(x = rnorm(100, 100, 15))

ggplot(a, aes(x)) + 
  stat_density(geom="line", size=1, color="dodgerblue") +
  theme_bw()
```

#####

```{r global_options, include=F, warning=F, message=F, echo=F, error=F}

# standard figure size and generate clean output
knitr::opts_chunk$set(fig.width=10, fig.height=8, warning=FALSE, message=FALSE, cache=TRUE, error=T, echo=F)

```

```{r, include=F, warning=F, message=F, echo=F, error=F}
#source("code/00 BPPS - workflowr prep.R")

packages <- c("arm", "BMA", "brms", "corrplot", "dummies","DescTools", "estimatr","extrafont", "extrafontdb", "janitor", "reshape2","tidyr","broom", "haven", "HH","Hmisc","lubridate","knitr", "margins", "magrittr", "plotrix", "scales","survey", "srvyr", "sysfonts", "foreign","car", "ICC", "PowerUpR", "openxlsx", "ggrepel", "readr", "readxl", "sjmisc", "sjPlot", "sjstats", "sjlabelled", "skimr","labelled", "texreg", "janitor","psych","dplyr", "tidyverse", "bbplot", "viridis", "here", "ggridges", "ggthemes", "DT", "jtools", "huxtable", "stringi", "gghighlight", "plm", "rethinking" , "brms", "rstan", "rstanarm","tidybayes","texreg","gt","gtsummary","huxtable","stargazer", "gsynth", "panelView", "assertr", "pointblank", "validate", "sandwich", "knitr", "kableExtra", "formattable")

lapply(packages, library, character.only=T)

font_add_google("Source Sans Pro", "sans-serif")

options(digits=4, scipen=6)

# set default
theme_set(theme_bw() + theme(panel.grid.minor.x=element_blank(),
                             panel.grid.minor.y=element_blank(),
                             plot.title=element_text(face="bold",size=18, hjust=.5, family = "Source Sans Pro"),
                             plot.subtitle = element_text(size=16, family="Source Sans Pro"),
                             plot.caption=element_text(size=12, family="Source Sans Pro"),
                             axis.title=element_text(size=16, family="Source Sans Pro"),
                             axis.text=element_text(size=14, family="Source Sans Pro"),    
                             legend.text=element_text(size=14, family="Source Sans Pro"),
                             strip.text=element_text(size=14, family="Source Sans Pro"))) 


# without border
base_style <- function(){theme_bw() +
    theme(panel.grid.minor.x=element_blank(),
          panel.grid.minor.y=element_blank(),
          plot.title=element_text(face="bold",size=18, hjust=.5, family = "Source Sans Pro"),
          plot.subtitle = element_text(size=16, family="Source Sans Pro"),
          plot.caption=element_text(size=12, family="Source Sans Pro"),
          axis.title=element_text(size=16, family="Source Sans Pro"),
          axis.text=element_text(size=14, family="Source Sans Pro"),    
          legend.text=element_text(size=14, family="Source Sans Pro"),
          strip.text=element_text(size=14, family="Source Sans Pro"),
          panel.border=element_blank(),
          axis.ticks = element_blank()) 
}

# path <- "../BPPS analysis/data/BPPS hh instrument pre-codebook.xlsx"
path <- "data/BPPS hh instrument pre-codebook.xlsx"


labs <- path %>%
  excel_sheets() %>%
  set_names() %>%
  lapply(function(x) read_xlsx(x, path=path))

lablist <- names(labs) %>%
  as.data.frame()

yes <- labs$yes_no
agree4 <- labs$agree4

# dat <- read_rds("../BPPS analysis/data/prepared/BPPS prepared.rds")
dat <- read_rds("data/prepared/BPPS prepared.rds")

svydat <- svydesign(data = dat,
                    ids= ~PSU + A9,
                    strata = ~strata,
                    weights = ~Wgt1)


svyrdat <- dat %>%
  as_survey_design(ids= PSU,
                   strata=strata,
                   weights=Wgt1)
```

## Module B.Awareness of USAID 



### B1. Are you aware of the United States Agency for International Development (USAID)? 

```{r}
b1 <- svyrdat %>%
  group_by(B1) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("B1" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

b1

```

### B2.	What are the main activities of USAID in Afghanistan?  

```{r}
get_labels(dat$B2c)
frq(dat$B2a)


```

### B3. Why do you think the United States Government provides this support to the Government of Afghanistan?

#### To help reduce poverty

```{r}
b3_a <- svyrdat %>%
  group_by(B3a) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(agree4,
            by=c("B3a" = "agree4_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=agree4_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

b3_a
```

#### To strengthen the friendship between the people of the United States and the people of Afghanistan

```{r}
b3_b <- svyrdat %>%
  group_by(B3b) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(agree4,
            by=c("B3b" = "agree4_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=agree4_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b3_b
```

#### To gain access to Afghanistan’s natural resources

```{r}
b3_c <- svyrdat %>%
  group_by(B3c) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(agree4,
            by=c("B3c" = "agree4_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=agree4_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b3_c
```

#### To strengthen the ability of the government of Afghanistan to serve its citizens

```{r}
b3_d <- svyrdat %>%
  group_by(B3d) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(agree4,
            by=c("B3d" = "agree4_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=agree4_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b3_d
```

### B4. Would you say your impression of USAID is positive or negative?

```{r}
positive <- labs$postive_negative

b4 <- svyrdat %>%
  group_by(B4) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(positive,
            by=c("B4" = "USAID_impress")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=positive_negative_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b4
```

### B5a. Why do you have a negative impression?

```{r}
reason1 <- get_labels(dat$B5a) %>%
  as.data.frame() %>%
  left_join(as.data.frame(frq(dat$B5a)), by=c(.="label")) %>%
  select(val,".") %>%
  rename(reason = ".",
         code = val) 


b5.a <- svyrdat %>%
  group_by(B5a) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(reason1,
            by=c("B5a" = "code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=reason, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b5.a
```

### B5b. Why do you have a positive impression?

```{r}
reason2 <- get_labels(dat$B5b) %>%
  as.data.frame() %>%
  left_join(as.data.frame(frq(dat$B5b)), by=c(.="label")) %>%
  select(val,".") %>%
  rename(reason = ".",
         code = val) 


b5.b <- svyrdat %>%
  group_by(B5b) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(reason2,
            by=c("B5b" = "code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=reason, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b5.b
```

### B6. Compared to one year ago, would you say your impression of USAID has worsened, remained the same, or improved?

```{r}
improve <- labs$improve

b6 <- svyrdat %>%
  group_by(B6) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(improve,
            by=c("B6" = "improve_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=improve_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b6
```

### B7. We’d like to get a sense of your knowledge of the different logos of donor governments and implementing organizations working in Afghanistan. I will show you a logo; please tell me whether you ever recall seeing that logo. 

#### United States Agency for International Development (USAID)

```{r}
b7a <- svyrdat %>%
  group_by(B7a) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("B7a" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b7a
```

#### German Society for International Cooperation (GIZ)

```{r}
b7b <- svyrdat %>%
  group_by(B7b) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("B7b" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b7b
```

#### People in Need (PIN)

```{r}
b7c <- svyrdat %>%
  group_by(B7c) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("B7c" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b7c
```

#### Department for International Development (DfID)

```{r}
b7d <- svyrdat %>%
  group_by(B7d) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("B7d" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b7d
```

#### Norwegian Refugee Council (NRC)

```{r}
b7e <- svyrdat %>%
  group_by(B7e) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("B7e" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b7e
```

#### Japan International Cooperation Agency (JICA)

```{r}
b7f <- svyrdat %>%
  group_by(B7f) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("B7f" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b7f
```

#### Canada International Development Agency (CIDA)

```{r}
b7g <- svyrdat %>%
  group_by(B7g) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("B7g" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b7g
```

#### Aga Khan Foundation

```{r}
b7h <- svyrdat %>%
  group_by(B7h) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("B7h" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b7h
```

#### Sweden International Development Agency (Sida)

```{r}
b7i <- svyrdat %>%
  group_by(B7i) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("B7i" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b7i
```

#### European Union (EU)

```{r}
b7j <- svyrdat %>%
  group_by(B7j) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("B7j" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b7j
```

#### International Office for Migration (IOM)

```{r}
b7k <- svyrdat %>%
  group_by(B7k) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("B7k" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b7k
```

### B8. If you have ever seen the logo, please try to identify what government donor or implementing organization is associated with each logo.

#### United States Agency for International Development (USAID)

```{r}
b8a <- svyrdat %>%
  group_by(B8a) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("B8a" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b8a
```

#### German Society for International Cooperation (GIZ)

```{r}
b8b <- svyrdat %>%
  group_by(B8b) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("B8b" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b8b
```

#### People in Need (PIN)

```{r}
b8c <- svyrdat %>%
  group_by(B8c) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("B8c" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b8c
```

#### Department for International Development (DfID)

```{r}
b8d <- svyrdat %>%
  group_by(B8d) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("B8d" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b8d
```

#### Norwegian Refugee Council (NRC)

```{r}
b8e <- svyrdat %>%
  group_by(B8e) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("B8e" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b8e
```

#### Japan International Cooperation Agency (JICA)

```{r}
b8f <- svyrdat %>%
  group_by(B8f) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("B8f" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b8f
```

#### Canada International Development Agency (CIDA)

```{r}
b8g <- svyrdat %>%
  group_by(B8g) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("B8g" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b8g
```

#### Aga Khan Foundation

```{r}
b8h <- svyrdat %>%
  group_by(B8h) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("B8h" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b8h
```

#### Sweden International Development Agency (Sida)

```{r}
b8i <- svyrdat %>%
  group_by(B8i) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("B8i" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b8i
```

#### European Union (EU)

```{r}
b8j <- svyrdat %>%
  group_by(B8j) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("B8j" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b8j
```

#### International Office for Migration (IOM)

```{r}
b8k <- svyrdat %>%
  group_by(B8k) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("B8k" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals = 0)
b8k
```
