---
title: "module-C"
author: "dkillian"
date: "2020-12-15"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction

Text explaining Module B: Awareness of USAID

#####

```{r global_options, include=F, warning=F, message=F, echo=F, error=F}

# standard figure size and generate clean output
knitr::opts_chunk$set(fig.width=10, fig.height=8, warning=FALSE, message=FALSE, cache=TRUE, error=T, echo=F)

```

```{r, include=F, warning=F, message=F, echo=F, error=F}
#source("code/00 BPPS - workflowr prep.R")

packages <- c("arm", "BMA", "brms", "corrplot", "dummies","DescTools", "estimatr","extrafont", "extrafontdb", "janitor", "reshape2","tidyr","broom", "haven", "HH","Hmisc","lubridate","knitr", "margins", "magrittr", "plotrix", "scales","survey", "srvyr", "sysfonts", "foreign","car", "ICC", "PowerUpR", "openxlsx", "ggrepel", "readr", "readxl", "sjmisc", "sjPlot", "sjstats", "sjlabelled", "skimr","labelled", "texreg", "janitor","psych","dplyr", "tidyverse", "bbplot", "viridis", "here", "ggridges", "ggthemes", "DT", "jtools", "huxtable", "stringi", "gghighlight", "plm", "rethinking" , "brms", "rstan", "rstanarm","tidybayes","texreg","gt","gtsummary","huxtable","stargazer", "gsynth", "panelView", "assertr", "pointblank", "validate", "sandwich", "knitr", "kableExtra", "formattable")

lapply(packages, library, character.only=T)

font_add_google("Source Sans Pro", "sans-serif")

options(digits=4, scipen=6)

# set default
theme_set(theme_bw() + theme(panel.grid.minor.x=element_blank(),
                             panel.grid.minor.y=element_blank(),
                             plot.title=element_text(face="bold",size=18, hjust=.5, family = "Source Sans Pro"),
                             plot.subtitle = element_text(size=16, family="Source Sans Pro"),
                             plot.caption=element_text(size=12, family="Source Sans Pro"),
                             axis.title=element_text(size=16, family="Source Sans Pro"),
                             axis.text=element_text(size=14, family="Source Sans Pro"),    
                             legend.text=element_text(size=14, family="Source Sans Pro"),
                             strip.text=element_text(size=14, family="Source Sans Pro"))) 


# without border
base_style <- function(){theme_bw() +
    theme(panel.grid.minor.x=element_blank(),
          panel.grid.minor.y=element_blank(),
          plot.title=element_text(face="bold",size=18, hjust=.5, family = "Source Sans Pro"),
          plot.subtitle = element_text(size=16, family="Source Sans Pro"),
          plot.caption=element_text(size=12, family="Source Sans Pro"),
          axis.title=element_text(size=16, family="Source Sans Pro"),
          axis.text=element_text(size=14, family="Source Sans Pro"),    
          legend.text=element_text(size=14, family="Source Sans Pro"),
          strip.text=element_text(size=14, family="Source Sans Pro"),
          panel.border=element_blank(),
          axis.ticks = element_blank()) 
}

# path <- "../BPPS analysis/data/BPPS hh instrument pre-codebook.xlsx"
path <- "data/BPPS hh instrument pre-codebook.xlsx"


labs <- path %>%
  excel_sheets() %>%
  set_names() %>%
  lapply(function(x) read_xlsx(x, path=path))

lablist <- names(labs) %>%
  as.data.frame()

yes <- labs$yes_no
agree4 <- labs$agree4

# dat <- read_rds("../BPPS analysis/data/prepared/BPPS prepared.rds")
dat <- read_rds("data/prepared/BPPS prepared.rds")

svydat <- svydesign(data = dat,
                    ids= ~PSU + A9,
                    strata = ~strata,
                    weights = ~Wgt1)


svyrdat <- dat %>%
  as_survey_design(ids= PSU,
                   strata=strata,
                   weights=Wgt1)
```

## Module C.Media 



### C1. Do you listen to radio programs? 

```{r}
c1 <- svyrdat %>%
  group_by(C1) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("C1" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals=0) %>%
  tab_header("C1. Listens to radio")

c1

```

### C2. How many days a week do you listen to radio programs?

```{r}
<<<<<<< HEAD
=======
#frq(dat$C2)
get_labels(dat$C2)
>>>>>>> f9317ee36395569abf59de08f0850cfc540c4f0c
days <- labs$days

c2 <- svyrdat %>%
  filter(C2<8) %>%
  group_by(C2) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(days,
            by=c("C2" = "days_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=days_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals=0) %>%
  tab_header("C2. Days per week listens to radio") %>%
  #tab_footnote(footnote="For n=3,030 (42.5%) who listen to radio",
               #locations=cells_column_labels(
                 #columns=vars(Percent))
               #) %>%
  tab_source_note("For n=3,030 (42.5%) who listen to radio")
  

c2
```

### C3. How many hours in a day do you listen to radio programs?

```{r}
<<<<<<< HEAD
hour_code <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,97,98,99)
hour_lab <- c("1 hour","2 hours","3 hours","4 hours","5 hours","6 hours","7 hours","8 hours","9 hours","10 hours","11 hours","12 hours","13 hours","14 hours","15 hours","16 hours","N/A","Refused","Don't know")
hours <- data.frame(hour_code, hour_lab)
=======
#frq(dat$C3)
hour_code <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,97,98,99)
hour_lab <- c("1 hour","2 hours","3 hours","4 hours","5 hours","6 hours","7 hours","8 hours","9 hours","10 hours","11 hours","12 hours","13 hours","14 hours","15 hours","16 hours","N/A","Refused","Don't know")
hours <- data.frame(hour_code, hour_lab)
#names(hours)
>>>>>>> f9317ee36395569abf59de08f0850cfc540c4f0c

c3 <- svyrdat %>%
  group_by(C3) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(hours,
            by=c("C3" = "hour_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=hour_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c3
```

### C4. Which radio stations do you listen to most often? 

#### First mention

```{r}
<<<<<<< HEAD
# frq(dat$C4a)
# frq(dat$C4b)
=======
#frq(dat$C4a)
#frq(dat$C4b)
>>>>>>> f9317ee36395569abf59de08f0850cfc540c4f0c

radio1 <- data.frame(frq(dat$C4a)) %>%
  filter(val!=97,
         val!=98,
         val!=99,
         frq>0) %>%
  arrange(desc(frq)) %>%
  mutate(raw.prc = frq/sum(frq),
         cum.prc=cumsum(raw.prc),
         code = val,
         radio_lab = label) %>%
  select(code,radio_lab)
<<<<<<< HEAD
# radio1
=======
#radio1
>>>>>>> f9317ee36395569abf59de08f0850cfc540c4f0c

c4a <- svyrdat %>%
  group_by(C4a) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(radio1,
            by=c("C4a" = "code")) %>% 
  na.omit %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=radio_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  arrange(desc(Sample)) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c4a
```

#### Second mention

```{r}
radio2 <- data.frame(frq(dat$C4b)) %>%
  filter(val!=97,
         val!=98,
         val!=99,
         frq>0) %>%
  arrange(desc(frq)) %>%
  mutate(raw.prc = frq/sum(frq),
         cum.prc=cumsum(raw.prc),
         code = val,
         radio_lab = label) %>%
  select(code,radio_lab)
radio2

c4b <- svyrdat %>%
  group_by(C4b) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(radio2,
            by=c("C4b" = "code")) %>% 
  na.omit %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=radio_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c4b
```


### C5.Are there any specific radio shows that you listen to regularly? 

#### First mention

```{r}
frq(dat$C5a)

show1 <- data.frame(frq(dat$C5a)) %>%
  filter(val!=97,
         val!=98,
         val!=99,
         frq>0) %>%
  arrange(desc(frq)) %>%
  mutate(raw.prc = frq/sum(frq),
         cum.prc=cumsum(raw.prc),
         code = val,
         show_lab = label) %>%
  select(code,show_lab)
show1

c5a <- svyrdat %>%
  group_by(C5a) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(show1,
            by=c("C5a" = "code")) %>% 
  na.omit %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=show_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c5a
```

#### Second mention

```{r}
show2 <- data.frame(frq(dat$C5b)) %>%
  filter(val!=97,
         val!=98,
         val!=99,
         frq>0) %>%
  arrange(desc(frq)) %>%
  mutate(raw.prc = frq/sum(frq),
         cum.prc=cumsum(raw.prc),
         code = val,
         show_lab = label) %>%
  select(code,show_lab)
show2

c5b <- svyrdat %>%
  group_by(C5b) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(show2,
            by=c("C5b" = "code")) %>% 
  na.omit %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=show_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c5b
```

### C6. Do you watch television?  

```{r}
frq(dat$C6)

c6 <- svyrdat %>%
  group_by(C6) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("C6" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c6
```

### C7. How many days a week do you watch television? 

```{r}
frq(dat$C7)

c7 <- svyrdat %>%
  group_by(C2) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(days,
            by=c("C2" = "days_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=days_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c7
```

### C8. How many hours in a day do you watch television? 

```{r}
frq(dat$C8)

c8 <- svyrdat %>%
  group_by(C8) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(hours,
            by=c("C8" = "hour_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=hour_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c8
```

### C9. Which television stations do you watch most often? 

#### First mention

```{r}
frq(dat$C9a)
frq(dat$C9b)

tv1 <- data.frame(frq(dat$C9a)) %>%
  filter(val!=97,
         val!=98,
         val!=99,
         frq>0) %>%
  arrange(desc(frq)) %>%
  mutate(raw.prc = frq/sum(frq),
         cum.prc=cumsum(raw.prc),
         code = val,
         tv_lab = label) %>%
  select(code,tv_lab)
tv1

c9a <- svyrdat %>%
  group_by(C9a) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(tv1,
            by=c("C9a" = "code")) %>%
  na.omit %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=tv_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c9a
```

#### Second mention

```{r}
tv2 <- data.frame(frq(dat$C9b)) %>%
  filter(val!=97,
         val!=98,
         val!=99,
         frq>0) %>%
  arrange(desc(frq)) %>%
  mutate(raw.prc = frq/sum(frq),
         cum.prc=cumsum(raw.prc),
         code = val,
         tv_lab = label) %>%
  select(code,tv_lab)
tv2

c9b <- svyrdat %>%
  group_by(C9b) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(tv2,
            by=c("C9b" = "code")) %>%
  na.omit %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=tv_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c9b
```

### C10. Are there any specific television shows that you watch regularly? 

#### First mention

```{r}
frq(dat$C10a)

tvshow1 <- data.frame(frq(dat$C10a)) %>%
  filter(val!=97,
         val!=98,
         val!=99,
         frq>0) %>%
  arrange(desc(frq)) %>%
  mutate(raw.prc = frq/sum(frq),
         cum.prc=cumsum(raw.prc),
         code = val,
         tvshow_lab = label) %>%
  select(code,tvshow_lab)
tvshow1

c10a <- svyrdat %>%
  group_by(C10a) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(tvshow1,
            by=c("C10a" = "code")) %>%
  na.omit %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=tvshow_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c10a
```

#### Second mention

```{r}
tvshow2 <- data.frame(frq(dat$C10b)) %>%
  filter(val!=97,
         val!=98,
         val!=99,
         frq>0) %>%
  arrange(desc(frq)) %>%
  mutate(raw.prc = frq/sum(frq),
         cum.prc=cumsum(raw.prc),
         code = val,
         tvshow_lab = label) %>%
  select(code,tvshow_lab)
tvshow2

c10b <- svyrdat %>%
  group_by(C10b) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(tvshow2,
            by=c("C10b" = "code")) %>%
  na.omit %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=tvshow_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c10b
```

### C11. Does this household have access to internet, either through a cable connection or cellular data? 

```{r}
c11 <- svyrdat %>%
  group_by(C11) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("C11" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c11
```

### C12. About how often do you engage with friends and family on social networking sites about social or political issues?

```{r}
rate <- labs$rate
names(rate)
c12 <- svyrdat %>%
  group_by(C12) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(rate,
            by=c("C12" = "rate_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = rate_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c12
```

### C.13 When you use social networking sites, which social networking sites do you most commonly use to engage friends and family about social or political issues? 

#### Facebook

```{r}
media <- labs$social_media
media
names(media)
a <- data.frame(frq(dat$C13_1))
a
b <- data.frame(frq(dat$C13_2))
b
frq(dat$C13_15)
c13_1 <- svyrdat %>%
  group_by(C13_1) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(media,
            by=c("C13_1" = "social_media_site")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = social_media_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c13_1
```

#### Twitter

```{r}
c13_2 <- svyrdat %>%
  group_by(C13_2) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(media,
            by=c("C13_2" = "social_media_site")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = social_media_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c13_2
```

#### Instagram

```{r}
c13_3 <- svyrdat %>%
  group_by(C13_3) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(media,
            by=c("C13_3" = "social_media_site")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = social_media_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c13_3
```

#### WhatsApp

```{r}
c13_4 <- svyrdat %>%
  group_by(C13_4) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(media,
            by=c("C13_4" = "social_media_site")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = social_media_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c13_4
```

#### SnapChat

```{r}
c13_5 <- svyrdat %>%
  group_by(C13_5) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(media,
            by=c("C13_5" = "social_media_site")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = social_media_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c13_5
```

#### Viber

```{r}
c13_6 <- svyrdat %>%
  group_by(C13_6) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(media,
            by=c("C13_6" = "social_media_site")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = social_media_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c13_6
```

#### Telegram

```{r}
c13_7 <- svyrdat %>%
  group_by(C13_7) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(media,
            by=c("C13_7" = "social_media_site")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = social_media_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c13_7
```

#### BOTIM

```{r}
c13_8 <- svyrdat %>%
  group_by(C13_8) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(media,
            by=c("C13_8" = "social_media_site")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = social_media_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c13_8
```

#### TikTok

```{r}
c13_9 <- svyrdat %>%
  group_by(C13_9) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(media,
            by=c("C13_9" = "social_media_site")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = social_media_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c13_9
```

#### LinkedIn

```{r}
c13_10 <- svyrdat %>%
  group_by(C13_10) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(media,
            by=c("C13_10" = "social_media_site")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = social_media_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c13_10
```

#### Pinterest

```{r}
c13_11 <- svyrdat %>%
  group_by(C13_11) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(media,
            by=c("C13_11" = "social_media_site")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = social_media_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c13_11
```

#### V Chat

```{r}
c13_12 <- svyrdat %>%
  group_by(C13_12) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(media,
            by=c("C13_12" = "social_media_site")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = social_media_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c13_12
```

#### VKntakte

```{r}
c13_13 <- svyrdat %>%
  group_by(C13_13) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(media,
            by=c("C13_13" = "social_media_site")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = social_media_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c13_13
```

#### Reddit

```{r}
c13_14 <- svyrdat %>%
  group_by(C13_14) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(media,
            by=c("C13_14" = "social_media_site")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = social_media_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c13_14
```

#### Other

```{r}
o1 <- data.frame(frq(dat$C13_15)) %>%
  select(val,label) %>%
  na.omit()

c13_15 <- svyrdat %>%
  group_by(C13_15) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(o1,
            by=c("C13_15" = "val")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = label, 
         Percent,
         `Margin of error`,
         Sample) %>%
  na.omit() %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c13_15
```

#### Other

```{r}
o2 <- data.frame(frq(dat$C13_16)) %>%
  select(val,label) %>%
  na.omit()

c13_16 <- svyrdat %>%
  group_by(C13_16) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(o2,
            by=c("C13_16" = "val")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = label, 
         Percent,
         `Margin of error`,
         Sample) %>%
  na.omit() %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c13_16
```

### C14. In the past year, how often have you visited the website or social networking page of any government office or ministry? 

```{r}
frq(dat$C14)

c14 <- svyrdat %>%
  group_by(C14) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(rate,
            by=c("C14" = "rate_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = rate_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c14
```

### C15a. How often does the household consult [media source] for news and information?

#### Radio
```{r}
frq(dat$C15Aa)
often <- labs$often

c15Aa <- svyrdat %>%
  group_by(C15Aa) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(often,
            by=c("C15Aa" = "often")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = often_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c15Aa
```

#### Television

```{r}
c15Ab <- svyrdat %>%
  group_by(C15Ab) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(often,
            by=c("C15Ab" = "often")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = often_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c15Ab
```

#### Newspaper

```{r}
c15Ac <- svyrdat %>%
  group_by(C15Ac) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(often,
            by=c("C15Ac" = "often")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = often_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)
c15Ac
```

#### Pamphlets / brochures

```{r}
c15Ad <- svyrdat %>%
  group_by(C15Ad) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(often,
            by=c("C15Ad" = "often")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = often_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c15Ad
```

#### Posters / Billboards

```{r}
c15Ae <- svyrdat %>%
  group_by(C15Ae) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(often,
            by=c("C15Ae" = "often")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = often_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c15Ae
```

#### Internet

```{r}
c15Af <- svyrdat %>%
  group_by(C15Af) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(often,
            by=c("C15Af" = "often")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = often_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c15Af
```

#### Social media

```{r}
c15Ag <- svyrdat %>%
  group_by(C15Ag) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(often,
            by=c("C15Ag" = "often")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = often_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c15Ag
```

#### Mosque

```{r}
c15Ah <- svyrdat %>%
  group_by(C15Ah) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(often,
            by=c("C15Ah" = "often")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = often_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c15Ah
```

#### Elders / Shuras

```{r}
c15Ai <- svyrdat %>%
  group_by(C15Ai) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(often,
            by=c("C15Ai" = "often")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = often_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c15Ai
```

#### Friends and family

```{r}
c15Aj <- svyrdat %>%
  group_by(C15Aj) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(often,
            by=c("C15Aj" = "often")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = often_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c15Aj
```


### 15b. Have you seen any message from USAID from that media source in the past year?

#### Radio
```{r}
frq(dat$C15Ba)
often <- labs$often

c15Ba <- svyrdat %>%
  group_by(C15Ba) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("C15Ba" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c15Ba
```

#### Television

```{r}
c15Bb <- svyrdat %>%
  group_by(C15Bb) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("C15Bb" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c15Bb
```

#### Newspaper

```{r}
c15Bc <- svyrdat %>%
  group_by(C15Bc) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("C15Bc" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c15Bc
```

#### Pamphlets / brochures

```{r}
c15Bd <- svyrdat %>%
  group_by(C15Bd) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("C15Bd" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c15Bd
```

#### Posters / Billboards

```{r}
c15Be <- svyrdat %>%
  group_by(C15Be) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("C15Be" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c15Be
```

#### Internet

```{r}
c15Bf <- svyrdat %>%
  group_by(C15Bf) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("C15Bf" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c15Bf
```

#### Social media

```{r}
c15Bg <- svyrdat %>%
  group_by(C15Bg) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("C15Bg" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c15Bg
```

#### Mosque

```{r}
c15Bh <- svyrdat %>%
  group_by(C15Bh) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("C15Bh" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c15Bh
```

#### Elders / Shuras

```{r}
c15Bi <- svyrdat %>%
  group_by(C15Bi) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("C15Bi" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c15Bi
```

#### Friends and family

```{r}
c15Bj <- svyrdat %>%
  group_by(C15Bj) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("C15Bj" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c15Bj
```

### C16. You mentioned reading, seeing, or hearing a message about USAID in the media sources you have used in the past year. Can you describe in a few words the content of that message?  

```{r}
frq(dat$C16)
message <- data.frame(frq(dat$C16)) %>%
  select(val,label)

c16 <- svyrdat %>%
  group_by(C16) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(message,
            by=c("C16" = "val")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = label, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c16
```

### C17. Regarding the USAID message or messages that you described, would you say that you have a very negative or positive impression of the message or messages? Is that somewhat or very negative or positive impression?

```{r}
c17 <- svyrdat %>%
  group_by(C17) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(positive,
            by=c("C17" = "USAID_impress")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = positive_negative_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)

c17
```

### C18a. Why do you have a negative impression?

```{r}
frq(dat$C18a)
frq(dat$C18b)

bad_reason <- data.frame(frq(dat$C18a)) %>%
  select(val,label)

c18a <- svyrdat %>%
  group_by(C18a) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(bad_reason,
            by=c("C18a" = "val")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = label, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)
c18a
```

### 18b. Why do you have a positive impression? 

```{r}
good_reason <- data.frame(frq(dat$C18b)) %>%
  select(val,label)

c18b <- svyrdat %>%
  group_by(C18b) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(good_reason,
            by=c("C18b" = "val")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response = label, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1)
c18b
```

