---
title: "module-E"
author: "dkillian"
date: "2020-12-16"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

#####

```{r global_options, include=F, warning=F, message=F, echo=F, error=F}

# standard figure size and generate clean output
knitr::opts_chunk$set(fig.width=10, fig.height=8, warning=FALSE, message=FALSE, cache=TRUE, error=T, echo=F)

```

```{r, include=F, warning=F, message=F, echo=F, error=F}
#source("code/00 BPPS - workflowr prep.R")

packages <- c("arm", "BMA", "brms", "corrplot", "dummies","DescTools", "estimatr","extrafont", "extrafontdb", "janitor", "reshape2","tidyr","broom", "haven", "HH","Hmisc","lubridate","knitr", "margins", "magrittr", "plotrix", "scales","survey", "srvyr", "sysfonts", "foreign","car", "ICC", "PowerUpR", "openxlsx", "ggrepel", "readr", "readxl", "sjmisc", "sjPlot", "sjstats", "sjlabelled", "skimr","labelled", "texreg", "janitor","psych","dplyr", "tidyverse", "bbplot", "viridis", "here", "ggridges", "ggthemes", "DT", "jtools", "huxtable", "stringi", "gghighlight", "plm", "rethinking" , "brms", "rstan", "rstanarm","tidybayes","texreg","gt","gtsummary","huxtable","stargazer", "gsynth", "panelView", "assertr", "pointblank", "validate", "sandwich", "knitr", "kableExtra", "formattable")

lapply(packages, library, character.only=T)

font_add_google("Source Sans Pro", "sans-serif")

options(digits=4, scipen=6)

# set default
theme_set(theme_bw() + theme(panel.grid.minor.x=element_blank(),
                             panel.grid.minor.y=element_blank(),
                             plot.title=element_text(face="bold",size=18, hjust=.5, family = "Source Sans Pro"),
                             plot.subtitle = element_text(size=16, family="Source Sans Pro"),
                             plot.caption=element_text(size=12, family="Source Sans Pro"),
                             axis.title=element_text(size=16, family="Source Sans Pro"),
                             axis.text=element_text(size=14, family="Source Sans Pro"),    
                             legend.text=element_text(size=14, family="Source Sans Pro"),
                             strip.text=element_text(size=14, family="Source Sans Pro"))) 


# without border
base_style <- function(){theme_bw() +
    theme(panel.grid.minor.x=element_blank(),
          panel.grid.minor.y=element_blank(),
          plot.title=element_text(face="bold",size=18, hjust=.5, family = "Source Sans Pro"),
          plot.subtitle = element_text(size=16, family="Source Sans Pro"),
          plot.caption=element_text(size=12, family="Source Sans Pro"),
          axis.title=element_text(size=16, family="Source Sans Pro"),
          axis.text=element_text(size=14, family="Source Sans Pro"),    
          legend.text=element_text(size=14, family="Source Sans Pro"),
          strip.text=element_text(size=14, family="Source Sans Pro"),
          panel.border=element_blank(),
          axis.ticks = element_blank()) 
}

# path <- "../BPPS analysis/data/BPPS hh instrument pre-codebook.xlsx"
path <- "data/BPPS hh instrument pre-codebook.xlsx"


labs <- path %>%
  excel_sheets() %>%
  set_names() %>%
  lapply(function(x) read_xlsx(x, path=path))

lablist <- names(labs) %>%
  as.data.frame()

yes <- labs$yes_no
agree4 <- labs$agree4

# dat <- read_rds("../BPPS analysis/data/prepared/BPPS prepared.rds")
dat <- read_rds("data/prepared/BPPS prepared.rds")

svydat <- svydesign(data = dat,
                    ids= ~PSU + A9,
                    strata = ~strata,
                    weights = ~Wgt1)


svyrdat <- dat %>%
  as_survey_design(ids= PSU,
                   strata=strata,
                   weights=Wgt1)
```


#### E1. Overall, based on your experience, do you think things in Afghanistan today are going in the right direction, or do you think they are going in the wrong direction?  


```{r}
direction <- labs$direction

#frq(dat$E1)

e1 <- svyrdat %>%
  group_by(E1) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(direction,
            by=c("E1" = "direction")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=direction_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals=0) %>%
  tab_header("E1. Direction of Afghanistan") 

e1

```


#### E2. Thinking of the different levels of government in Afghanistan, do you think that overall the [level of government] is doing a very bad job, somewhat bad job, somewhat good job, or a very good job? 

a. National government

```{r}
job <- labs$job
#job

#frq(dat$E2a)

e2a <- svyrdat %>%
  group_by(E2a) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(job,
            by=c("E2a" = "job")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=job_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals=0) %>%
  tab_header("a) National government performance") 

e2a

```


b. Provincial government

```{r}
#job <- labs$job

#frq(dat$E2a)

e2b <- svyrdat %>%
  group_by(E2b) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(job,
            by=c("E2b" = "job")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=job_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals=0) %>%
  tab_header("a) Provincial government performance") 

e2b

```


c. District government

```{r}

#frq(dat$E2c)

e2c <- svyrdat %>%
  group_by(E2c) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(job,
            by=c("E2c" = "job")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=job_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals=0) %>%
  tab_header("a) District government performance") 

e2c

```



#### E3. Are you aware of the peace agreement signed between the US Government and the Taliban in February of 2020? 


```{r}

#frq(dat$E3)

e3 <- svyrdat %>%
  group_by(E3) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  left_join(yes,
            by=c("E3" = "yes_no_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals=0) %>%
  tab_header("E3. Aware of US-Taliban peace agreement") 

e3

```


#### E4. As a result of implementation of the peace agreement between the USG and Taliban, do you think security in your area has worsened, remained the same, or improved? 


```{r}
better <- labs$better
#better

#frq(dat$E2a)

e4 <- svyrdat %>%
  group_by(E4) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  filter(E4!=97) %>%
  left_join(better,
            by=c("E4" = "better_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=better_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals=0) %>%
  tab_header("E4. Security after USG-Taliban peace agreement") %>%
  tab_source_note("For n=5,252 (73.7%) who are aware of the agreement")

e4

```


#### E5. As a result of the implementation of the peace agreement between the USG and Taliban, do you think that USAID support for the development of Afghanistan has decreased, remained the same, or increased? 


```{r}
increase <- labs$increase
#increase

#frq(dat$E2a)

e5 <- svyrdat %>%
  group_by(E5) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  filter(E5!=97) %>%
  left_join(increase,
            by=c("E5" = "peace_support")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=increase_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals=0) %>%
  tab_header("E5. USAID support after US-Taliban peace agreement") %>%
  tab_source_note("For n=5,252 (73.7%) who are aware of the agreement")

e5

```


#### E6. As a result of implementation of the peace agreement between the USG and Taliban, would you say that you are pessimistic or optimistic about the future of Afghanistan?


```{r}
opt <- labs$optimism
#opt

#frq(dat$E2a)

e6 <- svyrdat %>%
  group_by(E6) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  filter(E6!=97) %>%
  left_join(opt,
            by=c("E6" = "optimism_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=optimism_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals=0) %>%
  tab_header("E6. Outlook on Afghanistan after US-Taliban agreement") %>%
  tab_source_note("For n=5,252 (73.7%) who are aware of the agreement")

e6

```


#### E7. As a result of implementation of the peace agreement between the U.S. Government and the Taliban, would you say that the Taliban have become less influential or more influential in the governance of Afghanistan? 


```{r}
inf <- labs$influential
#inf

#frq(dat$E2a)

e7 <- svyrdat %>%
  group_by(E7) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  filter(E7!=97) %>%
  left_join(inf,
            by=c("E7" = "peace_influential")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=influential_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals=0) %>%
  tab_header("E7. Taliban influence after US-Taliban peace agreement") %>%
  tab_source_note("For n=5,252 (73.7%) who are aware of the agreement")

e7

```


#### E8. The peace agreement between the US and Taliban calls for direct negotiations between the Taliban and the Government of Afghanistan. Are you pessimistic or optimistic that the Government of Afghanistan and the Taliban will be able to negotiate a peace agreement?


```{r}
#increase <- labs$increase
#increase

#frq(dat$E2a)

e8 <- svyrdat %>%
  group_by(E8) %>%
  summarise(proportion = survey_mean(),
            total = survey_total()) %>%
  as.data.frame() %>%
  filter(E8!=97) %>%
  left_join(opt,
            by=c("E8" = "optimism_code")) %>%
  mutate(Percent=proportion,
         `Margin of error` = 1.96*proportion_se,
         Sample=round(total,0)) %>%
  select(Response=optimism_lab, 
         Percent,
         `Margin of error`,
         Sample) %>%
  gt() %>%
  fmt_percent(vars(Percent, `Margin of error`),
              decimals=1) %>%
  fmt_number(vars(Sample),
             decimals=0) %>%
  tab_header("E8. Prospects for GIRoA-Taliban peace agreement") %>%
  tab_source_note("For n=5,252 (73.7%) who are aware of the agreement")

e8

```




